\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-06-16 eg6-letters/NIM/author_list.tex
Add MB to authors
Update to elsevier framework

\affiliation{Argonne National Laboratory, Argonne IL 60439, USA}
\affiliation{Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and Universit$\acute{e}$ Paris Sud, Orsay, France}
\affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
%

\author{R.~Dupr\'e} \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}
\author{S.~Stepanyan} \affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
\author{M.~Hattawy} \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}
\author{N.~Baltzell} \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
\author{S.~Bueltmann} \affiliation{Old Dominion University, Norfolk, VA 23529, United States}
\author{A.~Celentano} \affiliation{INFN, Sezione di Genova, 16146 Genova, Italy}
\author{R.~De~Vita} \affiliation{INFN, Sezione di Genova, 16146 Genova, Italy}
\author{H.~Egiyan} \affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
\author{H.~Fenker} \affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
\author{K.~Hafidi} \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}
\author{S.~Kuhn} \affiliation{Old Dominion University, Norfolk, VA 23529, United States}
\author{Y.~Perrin} \affiliation{LPSC, Universit\'e Grenoble-Alpes, CNRS/IN2P3, Grenoble, France}
\author{B.~Torayev} \affiliation{Old Dominion University, Norfolk, VA 23529, United States}
\author{E.~Voutier} \affiliation{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}\affiliation{LPSC, Universit\'e Grenoble-Alpes, CNRS/IN2P3, Grenoble, France}
%\author{} \affiliation{}
%

\collaboration{The CLAS Collaboration} 
%
%\vskip 2.0cm

>>>>

\author[anl,ipn]{R.~Dupr\'e\corref{cor}}\ead{dupre@ipno.in2p3.fr} 
\author[jlab]{S.~Stepanyan} 
\author[anl,ipn]{M.~Hattawy} 
\author[anl,jlab]{N.~Baltzell} 
\author[anl]{K.~Hafidi} 
\author[infn]{M.~Battaglieri} 
\author[odu]{S.~Bueltmann} 
\author[infn]{A.~Celentano} 
\author[infn]{R.~De~Vita} 
\author[anl,utfsm]{A.~El~Alaoui} 
\author[msu]{L.~El~Fassi} 
\author[jlab]{H.~Egiyan} 
\author[jlab]{H.~Fenker} 
\author[anl]{K.~Kosheleva} 
\author[odu]{S.~Kuhn} 
\author[uc]{M.~Oliver} 
\author[lpsc]{Y.~Perrin} 
\author[odu]{B.~Torayev}
\author[ipn,lpsc]{E.~Voutier}

\address[anl]{Argonne National Laboratory, Argonne IL 60439, USA}
\address[ipn]{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}
\address[jlab]{Jefferson Laboratory, Newport News, VA 230606, USA}
\address[infn]{INFN, Sezione di Genova, 16146 Genova, Italy}
\address[odu]{Old Dominion University, Norfolk, VA 23529, United States}
\address[utfsm]{Universidad T\'ecnica Federico Santa Mar\'ia, Casilla 110-V Valpara\'iso, Chile}
\address[msu]{Mississippi State University, Mississippi State, MS 39762-5167}
\address[uc]{University of Chicago, Chicago, IL 60637, United States}
\address[lpsc]{LPSC, Universit\'e Grenoble-Alpes, CNRS/IN2P3, Grenoble, France}

\cortext[cor]{Corresponding author}
